### 2016-11-08 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home eds

Fig2 <- ddply(dd,
               .(Agemonths,LayYear),
               summarise,
               meanRTL = mean(RTL),
               n = length(RTL))  %>%
  ddply(.(LayYear),
        mutate,
        nAges = length(meanRTL),
        minAge = min(Agemonths)) %>%
  subset(minAge == 1) %>%
  subset(n > 5) %>%
  transform(Cohort = factor(LayYear)) %>%
  ggplot(aes(x = Agemonths,y = meanRTL,col = Cohort))+
  xlab('Age (months)') +
  geom_point()+
  geom_line()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

```{r Figure 4}
dd14$r <- sample(1:nrow(dd14),replace = F)
temp <- dd14[order(dd14$BirdID,dd14$r,decreasing = F),] %>%
  subset(!duplicated(BirdID)) %>%
  subset(Died == 1)

Fig4A <- ggplot(temp,
       aes(x = Sex,
           col = factor(SurvivedNext),
           y = RTL)) +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_boxplot(notch=T)
  annotate('text',x = 17,y = 2.5,label = 'C')

temp <- ddply(juv14,
              .(LayYear,Fledged),
              summarise,
              MeanTL = median(RTL),
              Survived = mean(SurvivedNext),
              n = length(RTL)) %>%
  subset(n > 9)

ggplot(temp,aes(x = MeanTL,y = Survived,col = Fledged))+
  geom_point()+
  stat_smooth(method = 'lm')

Fig4B <- ??

@@

x <- subset(dd14,Fledged == 'Fledglings')

table(x$Sex,x$LayYear)

dd14$SexAge <- paste(dd14$Fledged,dd14$Sex)

ggplot(dd14,aes(x = Tarsus,y = RTL,col = SexAge))+
geom_smooth(method = 'lm')

>>>>

Fig2A <- transform(juv,Cohort = factor(LayYear)) %>%
  subset(Agemonths>1) %>%
  ggplot(aes(y = RTL,x = Cohort))+
  xlab('Cohort') +
  geom_boxplot() +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

Fig2B <- ddply(dd,
               .(Agemonths,LayYear),
               summarise,
               meanRTL = mean(RTL),
               n = length(RTL))  %>%
  ddply(.(LayYear),
        mutate,
        nAges = length(meanRTL),
        minAge = min(Agemonths)) %>%
  subset(LayYear %in% c(2001:2009)) %>%
  subset(n>4) %>%
  transform(Cohort = factor(LayYear)) %>%
  ggplot(aes(x = Agemonths,y = meanRTL,col = Cohort))+
  xlab('Age (months)') +
  ylab('Mean RTL') +
  geom_point()+
  geom_line()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

```{r Figure 4}
Fig4A <- ggplot(dd14,
       aes(x = Agemonths,
           col = factor(SurvivedNext),
           y = RTL)) +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  geom_smooth(method = 'lm',formula = y~log(x))
  annotate('text',x = 17,y = 2.5,label = 'C')

Fig4B <- ggplot(dd8,
       aes(x = RTL,
           y = RemainingLife,
           col = Fledged)) +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  geom_smooth(method = 'lm')
  annotate('text',x = 17,y = 2.5,label = 'C')

@@
